---
output: 
  github_document:
    html_preview: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  fig.show = "hold",
  fig.retina = 2,
  out.width = "70%",
  #dev = "svg",
  message = FALSE,
  warning = FALSE
)
devtools::load_all()
```

```{r include=FALSE}
# a workaround to include htmlwidgets in github_document output format.
# This just generates the github-flavored markdown (.md) and then github
# generates on-the-fly the html from it. Thus htmlwidgets wont's work
# out-of-the-box. This solution is based on 
# https://stackoverflow.com/questions/61253015/render-ggplotly-in-r-markdown-github-document
# 
# yet, it will not work in github. Locally it works fine, but up there in 
# github, the github flavored markdown spec disallows some html tags, including
# <iframe> and therefore it will just show the code and not actually render the
# content of the iframe target
# https://github.github.com/gfm/#disallowed-raw-html-extension-
# Then, just webshot the htmlwidgets and make them a static image
iframe_htmlwidget <- function(htmlwidget) {
  
  html_path <- knitr::fig_path("html") # get the path like knitr would do
  # TODO: should I ensure this is always a relative path?
  #       it seems it is, but can't find assurances
  
  htmlwidgets::saveWidget(
    widget = htmlwidget, 
    file = normalizePath(html_path), # full path, otherwise it'll complain
    selfcontained = TRUE
    # selfcontained = TRUE, but still the dependencies are copied to te figures
    # dir so you need to exclude them via .gitignore to avoid commiting jquery,
    # plotly, and all other libraries in version control
  )
  
  # If local preview, you want the iframe to point to an absolute path because
  # "when you render from within RStudio using the Knit button the preview HTML 
  # is written to a temporary directory and then automatically displayed by 
  # RStudio.". 
  # https://rmarkdown.rstudio.com/github_document_format.html#HTML_Preview
  # 
  # They handle the images well, but they are not aware of the 
  # iframe, and therefore, the saved htmlwidget will not be found.
  # To overcome this, and absolute path in your system will do. However, that
  # won't work when it's online, so before pushing this to github, you should
  # set html_preview = FALSE and this little function will leave the iframe
  # with a relative path
  iframe_src_path <- ifelse(
    test = isTRUE(rmarkdown::metadata$output$github_document$html_preview),
    yes = normalizePath(html_path),
    no = html_path
  )

  htmltools::tags$iframe(
    src = iframe_src_path,
    width = "70%",
    height = "600",
    scrolling = "no",
    seamless = "seamless",
    frameBorder = "0",
    style = "display: block; margin: auto;"
  )
  # TODO: consider also not including assets in the html file but rather cdn links
  # see for example this SO question for ideas
  # https://stackoverflow.com/questions/51213463/how-to-skip-writing-dependencies-in-htmlwidgetssavewidget
  # plot_html_widget$dependencies[[2]]$src$file <- NULL
  # plot_html_widget$dependencies[[2]]$src$href <- "https://code.jquery.com/"s
}

# I guess this is another viable approach
# https://github.com/ropensci/plotly/issues/1620
# Basically use output: html_document: keep_md: true

# Need this little function to use webshot2
# Although plain webshot would be more convenient as rmarkdown would handle 
# it automatically, webshot does not get along good with plotly
webshotme <- function(htmlwidget, ...) {
  png_path <- knitr::fig_path("png") # get the path like knitr would do
  html_path <- tempfile(fileext = ".html")
  htmlwidgets::saveWidget(htmlwidget, file = html_path, selfcontained = TRUE)
  webshot2::webshot(html_path, file = png_path, ...)
}
```


# wdiquickplots

<!-- badges: start -->
<!-- badges: end -->

The goal of `wdiquickplots` is to provide, well, quick plots for World
Development Indicators (WDI, ["the primary World Bank collection of
development indicators, compiled from officially recognized international
sources."](https://databank.worldbank.org/home.aspx)).  To get WDI data, this
package is powered by [`WDI`](http://vincentarelbundock.github.io/WDI/) package,
developed by Vincent Arel-Bundock.

## Installation

You can install it from this Github repo with:

```r
remotes::install_github("edalfon/wdiquickplots")
```

## How to use it

Use case: hey I have to present this study I have been working on in my home
country to an audience where I currently live (studying abroad or whatever).
Thus, some background data on my home country is in order. A table would
certainly do, but it is boring. So let's put some plots in there.

```{r dist, fig.asp=870/550, fig.width=4.5, out.width="47%", dev="svg"}
library(wdiquickplots)
plot_dist_wdi("NY.GDP.PCAP.PP.CD", p = 0)
```

There you go. That's the spirit of this package. One line of code and bang!, 
a relatively decent plot that you can put in your slides to convey a quick 
message.

Using this package goes as follows:

- Find the code of the indicator of interest. You can use `WDI::WDIsearch` for
  this, but I actually find it a bit more user-friendly to simply go to the
  [indicators page
  (https://data.worldbank.org/indicator)](https://data.worldbank.org/indicator)
  and get the code from there (it's in the URL).
- You pass the indicator code as the first argument of the different plotting 
  functions in this package.
- As second argument, you pass the countries you want to highlight.

And that's it.

You can read other details and description of features [in the `pkgdown` site
for this little package](https://edalfon.github.io/wdiquickplots/) (I know, a
`pkgdown` site may be overkill, but anyway). [There you can also see examples
for all the quick plots in this
package](https://edalfon.github.io/wdiquickplots/docs/articles/wdiquickplots.html),
but in general, they quickly show:

- Where the highlighted countries stand in terms of the indicator of interest. 
- How do they compare among highlighted countries, and against the rest of the
  world, regions or income groups. 
- What have been the changes in time.
