---
title: "Features"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{features}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.retina = 2,
  out.width = "70%",
  fig.show = "hold",
  fig.align = "center",
  #dev = "svg",
  message = FALSE,
  warning = FALSE
)
```

This document describes a few features of the package and documents some
admittedly controversial design decisions.

```{r setup}
library(wdiquickplots)
```


# Features

## Facet by regions or World Bank's income groups

Some of the plots have facets and you can configure whether they group the data
by geographical regions or income groups. Simply pass unquoted `region` or 
`income` to the `facets` argument.

```{r dist, fig.asp=870/550, fig.width=5.5, out.width="45%", dev="svg", fig.ext = "svg", fig.align = "default"}
plot_dist_wdi_ind("NY.GDP.PCAP.PP.CD", facets = income, p = 0)
plot_dist_wdi_ind("NY.GDP.PCAP.PP.CD", facets = region, p = 0)
```

## Subsetting the data

By default, `wdiquickplots` shows the data for all countries available. But it 
provides three ways to subset the countries to include in the plot. There are
three arguments for this:

- `country` let's you arbitrarily select countries (1...*). We pass this 
  argument directly to WDI, hence you need to use ISO-2 character code to 
  indicate the countries (see `?WDI::WDI()`). As in WDI, this defaults to "all".
- `regions` let's you select a group of countries, indicating World Bank 
  regions. `wdiquickplots:::regions`
- `income_groups` let's you select a group of countries, indicating World 
  Bank's income classification. `wdiquickplots:::income`

```{r dist_subset, fig.asp=0.7, fig.width=5.5, out.width="77%", dev="svg", fig.ext = "svg"}
plot_dist_wdi_ind(
  indicator = "NY.GDP.PCAP.PP.CD", facets = region, p = 0, 
  regions = c("Europe & Central Asia", "Latin America & Caribbean")
)
```


# Watch out

## Latest available data point per country

In all plotting functions you can specify the period to download the data
(`start` and `end` year). However, some plots do not show the time series but
only one point in time per country. In those cases, **the default is to keep the
latest available data point for each country**.

This is to try to keep as many countries as possible in the data to plot.
So, instead of dropping countries with missing data for the last year, we would 
rather keep them and tolerate them with somewhat older data.

The implication is that the plot can contain non-comparable data, and
end-up mixing different years for different countries.

Of course, that can be controversial and certainly it is not ideal. To this, we
would say a couple of things:

- **You can always opt-out of this default and force `wdiquickplots` to show 
  the same year for all countries.**
  To do this, simply set `start` and `end` to the same value. Thus, you ensure 
  comparability. Just keep in mind that the countries without data for that 
  year will be simply dropped and not shown in the plot.
- **Sometimes it may be ok.**
  This is the default behavior because we think sometimes it is ok. For example,
  for some indicators that do not change much over time, it may be better to
  have older data points for some countries, than to drop them altogether. That
  way you can at least have an idea where all those countries stand, even though
  their data are somewhat old. So, in this sense we defend this behavior, but
  ...
- **The plots try to be transparent about it, and you should too.**
  All the plots where this is the case try to warn about the issue. But not many 
  details can be included in the plot because doing so, we would risk ending-up
  with an over-cluttered plot. Thus, the users of the plots should also warn
  their audience and be transparent about it.
  
## Further customization

Main features have been described already in this site. And some of the plots
allow for some more customization. But not much really. For example, the bar 
plot allows the user to customize the colors (see `?plot_bar_wdi_ind`) but you 
cannot turn it into a lollipop plot. In addition, you get the plot objects 
prepared by `wdiquickplots` (e.g. `ggplot2` object) and you can go wild (e.g.
override `scale_fill_brewer` to change color palette, you can even remove or
change facets).

And although you can do that, it is certainly not in line with the spirit of
this package. Quick plots!, if you have to fiddle too long with arguments and
trying to change too many things on the plot, it is not a quick plot anymore.
That would also indicate you need something different than the prefabricated
plots in this package. In those cases, you are probably better off using
directly `WDI` to get the data and make your own plot.

## Interpolation for a smooth race plot



## memoise

Although memoise does a great job, there's the famouse quote that there are only
two hard things, cache invalidation and naming things. So, if you find memoise is creating problems, just delete the cache as follows.
