---
title: "Quickplots examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickplots examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.show = "hold",
  fig.retina = 2,
  out.width = "70%",
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(wdiquickplots)
```


# Distribution

A plot to quickly compare highlighted countries, among them, and with the 
rest of the world using either region or income, to group countries.

```{r dist_gini, fig.asp=870/550, fig.width=6, out.width="47%", dev="svg", fig.ext="svg"}
plot_dist_wdi("NY.GDP.PCAP.PP.CD", p = 0)
```


# Bar plot

Similar as the distribution plot, quickly shows where the highlighted countries
stand in comparison with the rest of the world (without using any country
groups). This one is interactive so you can explore a bit (e.g. zooming in and 
out or see the exact value of the indicator for each country as tooltip).

```{r barplot}
plot_bar_wdi("NY.GDP.PCAP.PP.CD")
```

# Race bar plot

Takes the same approach as the bar plot above, but showing also how it changes 
over time (powered by `gganimate`).

```{r race, out.width="40%", fig.asp=550/350, fig.width=5, cache=FALSE}
plot_race_wdi("NY.GDP.PCAP.PP.CD")
```


# Line plot

Well, a line plot including only data from the highlighted countries. It shows 
directly the first and last value for each country and labels the series 
directly (it is an interactive plot as well).

```{r lineplot}
plot_time_wdi("NY.GDP.PCAP.PP.CD")
```


# Facetted line plot

Also a line plot as above, but including data for all countries.
It is powered by `gghighlight` to disentangle the spaghetti plot.

```{r time_facets, dev="svg", fig.ext="svg"}
plot_time_facets_wdi("NY.GDP.PCAP.PP.CD")
```

# Spaghetti plot

No one should ever see or want to see a spaghetti plot with so many series. 
Yet, here's one. 

Just have fun playing with it. The interactivity (powered by `dygraphs`)
highlights one series at a time, and sometimes (very rarely, but sometimes), can 
make such a spaghetti plot useful to identify eye-catching patterns.


```{r spaghetti}
plot_spaghetti_wdi("NY.GDP.PCAP.PP.CD")
```

# Bubble plot

A quick-to-create bubble plot. Basically a function to produce a scatter plot
and you pass the codes for the indicators you want in the x and y axis, as well
as the indicator to map the size of the markers to.

Let's see an example showing public health expenditure vs. risk of catastrophic 
health expenditure.

## Static

There is a static version, powered by `ggplot2`.

```{r bubble_gg, dev="svg", fig.ext="svg"}
plot_bubble_gg_wdi(
  x_indicator = "SH.XPD.GHED.GD.ZS",
  y_indicator = "SH.SGR.CRSK.ZS",
  size_indicator = "SP.POP.TOTL",
  highlight_countries = c("India", "Germany", "Brazil")
)
```

## Interactive

An although you can convert the static bubble plot to an interactive one 
(e.g. using plotly::ggplotly), those automatic conversions usually leave 
a few things that could be better. Thus, there is also an interactive version, 
powered by `plotly`.

```{r bubble_ly}
plot_bubble_ly_wdi(
  x_indicator = "SH.XPD.GHED.GD.ZS",
  y_indicator = "SH.SGR.CRSK.ZS",
  size_indicator = "SP.POP.TOTL",
  highlight_countries = c("India", "Germany", "Brazil")
)
```



# Animated bubble plot

And if you dare, you can throw one more dimension (time) to the bubble plot,
and make it an animated plot.


## Static

Again, there is static version powered by `ggplot2` and `gganimate`.

```{r bubble_anime_gg}
plot_bubble_anime_gg_wdi(
  x_indicator = "SH.XPD.GHED.GD.ZS",
  y_indicator = "SH.SGR.CRSK.ZS",
  size_indicator = "SP.POP.TOTL",
  highlight_countries = c("India", "Germany", "Brazil")
)
```

## Interactive

And a `plotly`-based version.

```{r bubble_anime_ly}
plot_bubble_anime_ly_wdi(
  x_indicator = "SH.XPD.GHED.GD.ZS",
  y_indicator = "SH.SGR.CRSK.ZS",
  size_indicator = "SP.POP.TOTL",
  highlight_countries = c("India", "Germany", "Brazil")
)
```
