---
title: "Quickplots examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{wdiquickplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.show = "hold",
  fig.retina = 2,
  out.width = "70%",
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(wdiquickplots)
```


# Distribution

A plot to quickly compare highlighted countries, among them, and with the 
rest of the world using either region or income, to group countries.

```{r dist_gini, fig.asp=870/550, fig.width=4, out.width="47%", dev="svg", fig.ext="svg"}
plot_dist_wdi_ind("NY.GDP.PCAP.PP.CD", p = 0)
```


# Bar plot

Similar as the distribution plot, quickly shows where the highlighted countries
stand in comparison with the rest of the world (without using any country
groups). This one is interactive so you can explore a bit (e.g. zooming in and 
out or see the exact value of the indicator for each country as tooltip).

```{r barplot}
plot_bar_wdi_ind("NY.GDP.PCAP.PP.CD")
```

# Race bar plot

Takes the same approach as the bar plot above, but showing also how it changes 
over time (powered by `gganimate`).

```{r race, out.width="40%", fig.asp=550/350, fig.width=5, cache=FALSE}
plot_race_wdi_ind("NY.GDP.PCAP.PP.CD")
```


# Line plot

Well, a line plot including only data from the highlighted countries. It shows 
directly the first and last value for each country and labels the series 
directly (it is an interactive plot as well).

```{r lineplot}
plot_time_wdi_ind("NY.GDP.PCAP.PP.CD")
```


# Facetted line plot

Also a line plot as above, but including data for all countries.
It is powered by `gghighlight` to disentangle the spaghetti plot.

```{r time_facets, dev="svg", fig.ext="svg"}
plot_time_facets_wdi_ind("NY.GDP.PCAP.PP.CD")
```

# Spaghetti plot

No one should ever see or want to see a spaghetti plot with so many series. 
Yet, here's one. `r emo::ji("see_no_evil_monkey")`.

Just have fun playing with it. The interactivity (powered by `dygraphs`)
highlights one series at a time, and sometimes (very rarely, but sometimes), can 
make such a spaghetti plot useful to identify eye-catching patterns.


```{r spaghetti}
plot_spaghetti_wdi_ind("NY.GDP.PCAP.PP.CD")
```




